\mireval{}

### 2014-05-08 paper/paper.tex
Not including pattern in table

The resulting average relative change for each metric is presented in Table \ref{tab:comparison}.
For may of the metrics, the average relative change is less than a few tenths of a percent, indicating that \mireval{} is equivalent up to rounding/precision errors.
In the following sections, we enumerate the known implementation differences which account for the larger average relative changes.

>>>>

The resulting average relative change for each metric is presented in Table \ref{tab:comparison}.
The average relative change for all of the pattern discovery metrics was 0, so they are not included in this table.
For many of the other metrics, the average relative change was less than a few tenths of a percent, indicating that \mireval{} is equivalent up to rounding/precision errors.
In the following sections, we enumerate the known implementation differences which account for the larger average relative changes.
